The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
hab perspect p1

## Habitat selection and space use
### 1
Habitat selection and shared space use *link to social*
Habitat selection depends on 
species specific
individual differences in home range and habitat selection
percentage of home range overlap links to foraging quality and availability in herbivores
multilayer networks are "a potential framework" for investigating social dynamics given shared space use and individual habitat selection

### 2
Sociality / multilayer have been used with habitat selection and space use
... examples

>>>>

## Habitat selection and space use
<!--
* Social structure is influenced by large scale processes such as resource availability and seasonality [@Peigner_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
* Habitat selection definition
* johnson's four scales of selection and Mayor 2009 habitat selection across scales
* habitat selection influences social structure since resource availability + quality influence home range size and overlap
* individuals must share space to interact [@Farine_2015]
* multilayer networks represent a novel framework for considering habitat selection and space use on sociality across scales

individual differences in habitat selection
-->

Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the "disproportionate use of
available" [@Mayor_2009] landscape resources or features by animals. Johnson
(1980) identified four orders of habitat selection: (1) the geographical range
of a species, (2) the home range of an individual, (3) the habitat patches
within the home range and (4) specific resources within a habitat patch.
Combined, habitat selection and social structure are intimately linked as
individuals must share space to interact [@Farine_2015] and resource
availability and quality influence home range size and overlap. Multilayer
networks represent a novel framework for considering the influence of habitat
selection and space use on sociality across scales.

### 2

Sociality / multilayer have been used with habitat selection and space use
... examples
